Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 Lemmas.tex
re-state lemmas/proofs in the appendix

>>>>

\section{Proof of Lemma~\ref{lem:no-incentives}}
\label{sec:lemma8-proof}

\begin{rlemma}{Lemma}{\ref{lem:no-incentives}}
Fix an arm $i$.
Let $s \geq \exp(2/\MinProb)$, and let $\tau_s$ be the (random)
time when arm $i$ is pulled for the \Kth{s} time.
Under \AccEU{\tau_s}{\frac{p}{4\Diam d \TieDensity}},
this pull of arm $i$ is not incentivized.
\end{rlemma}

\begin{proof}
By Lemma~\ref{lem:right-choice},
under the event \AccEU{\tau_s}{\frac{\MinProb}{4\Diam d \TieDensity}},
all agent types \AgV with
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
> \frac{\MinProb}{2\TieDensity}$
will pull their best arm \Best{\AgV}.

By Assmption~\ref{A1},
%Lemma~\ref{lem:sdelta},
the measure of agents (across all arms)
whose best and second-best arm differ in utility by less
than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
In particular, this bound holds for agents whose best arm is $i$.
By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
will myopically pull arm $i$.
Because $1/\log(s) < \frac{\MinProb}{2}$ for
$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
$\tau_s$.
\end{proof}

### 2018-02-17 algorithm.tex
re-state lemmas/proofs in the appendix

As a first step towards bound the total payment (and also regret),
we show that for sufficiently late phases,
under the event \AccEU{t}{x} for suitably small $x$,
the algorithm does not offer any payments.

@@

\begin{proof}
By Lemma~\ref{lem:right-choice},
under the event \AccEU{\tau_s}{\frac{\MinProb}{4\Diam d \TieDensity}},
all agent types \AgV with
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
> \frac{\MinProb}{2\TieDensity}$
will pull their best arm \Best{\AgV}.

By Assmption~\ref{A1},
%Lemma~\ref{lem:sdelta},
the measure of agents (across all arms)
whose best and second-best arm differ in utility by less
than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
In particular, this bound holds for agents whose best arm is $i$.
By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
will myopically pull arm $i$.
Because $1/\log(s) < \frac{\MinProb}{2}$ for
$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
$\tau_s$.
\end{proof}

>>>>

As a first step towards bound the total payment (and also regret),
we show that for sufficiently late phases,
under the event \AccEU{t}{x} for suitably small $x$,
the algorithm does not offer any payments. We prove Lemma~\ref{lem:no-incentives} in the Appendix~\ref{sec:lemma8-proof}.

@@
